---
title: "YCBM Analysis"
output: html_notebook
---

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(lubridate)
bookings <- read_csv("YCBM_export.csv")

true_bookings <- bookings %>% 
  filter("Profile", "Booking Made", "Start", "End", Cancelled==FALSE) %>%
  mutate(Start = ymd_hm(`Start (UTC)`), month=as.factor(month(Start, label=TRUE)), time_of_day = hour((Start - 8)) %% 24)
```

YouCanBook.me is a booking platform that allows customers to book meetings directly into Google calendars. It offers a personalized scheduling-page, allowing customers to easily book their appointments, and be notified upon them when the time arrives. 

This platform is fairly simple to setup: the user needs to connect a Google Calendar to the YCBM account, and set the required features. Users can then control their availability through their calendar and publish the new booking grid to a website or send a link by email. This allows customers to book an appointment according to their convenience. Automatic detailed notifications occur when a customer makes a booking and the booking will also go straight into the calendar. Customers can also reschedule their bookings, which will update automatically in the calendar.

We have been running YCBM since 2014

# Who are the meetings booked with?
```{r}
ggplot(true_bookings, aes(as.factor(Team), group=year, group=month, fill=month)) +
  geom_histogram(stat="count", position="dodge") + theme_bw() +
  xlab("") + ylab("")
```

# Where are the bookings from?
```{r}
ggplot(true_bookings, aes(`Booker Timezone`)) +
  geom_histogram(stat="count", position="dodge") + theme_bw() +
  xlab("") + ylab("") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# A priori quality
- generic email address = poor
- corporate email address = fair
- corporate email address with agenda in notes = good

```{r}
qual_bookings <- true_bookings %>%
  mutate(quality = ifelse(grepl("@gmail.com", EMAIL) | grepl("@qq.com", EMAIL), "poor", ifelse(
    is.na(NOTES), "fair", "good"
  )))

true_bookings$quality <- factor(true_bookings$quality, levels=c("poor", "fair", "good"))

ggplot(true_bookings, aes(month, fill=quality)) +
  geom_histogram(stat="count", position="dodge") + theme_bw() +
  xlab("") + ylab("") 
```

